---
title: "It's hard to plot Bayesian correlations"
author: "A Solomon Kurz"
date: "`r format(Sys.Date())`"
output: github_document
---

## Data

Simulate data for three variables with known correlations.

```{r, warning = F, message = F}
library(tidyverse)

m <- c(0, 0, 0)      # the means
s <- c(1, 1, 1)      # the sigmas
r <- c(.6, .1, -.5)  # the correlations

# here's the variance/covariance matrix
v <- 
  matrix(c((s[1] * s[1]),        (s[2] * s[1] * r[1]), (s[3] * s[1] * r[2]),
           (s[2] * s[1] * r[1]), (s[2] * s[2]),        (s[3] * s[2] * r[3]),
           (s[3] * s[1] * r[2]), (s[3] * s[2] * r[3]), (s[3] * s[3])),
         nrow = 3, ncol = 3)

# after setting our seed, we're ready to simulate with `mvtnorm::rmvnorm()`
set.seed(1)
d <- 
  mvtnorm::rmvnorm(n = 100, mean = m, sigma = v) %>% 
  data.frame() %>% 
  set_names(str_c("u_", 0:2))

head(d)
```

They look like this.

```{r, fig.width = 4.25, fig.height = 4}
d %>% 
  GGally::ggpairs()
```

## Model

Load brms and tidybayes.

```{r, warning = F, message = F}
library(brms)
library(tidybayes)
```

To get the correlation estimates, fit an intercepts-only multivariate model.

```{r fit, cache = T, warning = F, message = F, results = "hide"}
fit <- 
  brm(data = d, 
      family = gaussian,
      mvbind(u_0, u_1, u_2) ~ 1,
      prior = c(prior(normal(0, 1), class = Intercept),
                prior(normal(1, 1), class = sigma, resp = u0),
                prior(normal(1, 1), class = sigma, resp = u1),
                prior(normal(1, 1), class = sigma, resp = u2),
                prior(lkj(4), class = rescor)),
      chains = 4, cores = 4, 
      seed = 1,
      file = "fit")
```

Here are the model results.

```{r}
print(fit)
```

Here's a more focused look at the correlations.

```{r}
VarCorr(fit)$residual__$cor
```

## Get ready to plot

Here we'll extract the posterior samples for the correlations and summarize them with `tidybayes::median_qi()`.

```{r}
c <- 
  posterior_samples(fit) %>% 
  select(starts_with("rescor")) %>% 
  gather() %>% 
  group_by(key) %>% 
  median_qi(value)
  
print(c)
```

The names in `key` are a mess. Let's rearrange a bit.

```{r}
c <-
  c %>% 
  mutate(key = str_remove(key, "rescor__")) %>% 
  separate(key, into = c("l", "r"))

c
```

Now we'll repeat the estimates for the opposite sides of the diagonal.

```{r}
c <-
  c %>% 
  rename(l = r, 
         r = l) %>% 
  bind_rows(c)

c
```

Here's a way to plot the coefficients in a correlation-matrix-like presentation.

```{r, fig.width = 6.4, fig.height = 2.75}
c %>% 

  ggplot(aes(x = value, y = 0)) +
  geom_pointintervalh() +
  scale_y_discrete(NULL, position = "right") +
  xlab(expression(rho)) +
  coord_cartesian(xlim = -1:1) +
  theme(strip.background = element_blank(),
        strip.text.y     = element_text(angle = 180, hjust = 0),
        axis.text.y      = element_text(hjust = 0)) +
  facet_grid(l~r, switch = "y")
```

## Session info

```{r}
sessionInfo()
```

